Multiset-trie data structure

### 2022-08-17 tex/tex/s_conclusions.tex
s_conclusions updated.

The multiset-trie is an input-sensitive data structure because the size of multiset-trie $|\mathcal{M}|$ depends on the distribution of multisets in $M.$
Our mathematical model assumes that multisets $m$ in $M$ are distributed uniformly;  however, in real-world models, such an assumption is not generally true. 
%Specifically, the probability $P(m\in M)$ may vary dramatically and can even be equal to $0.$ For example, if words are mapped to multisets, then the sample space contains very large multisets. 
For example, many multisets will have zero probability of appearing in $M$ because a word that would correspond to such a multiset does not exist in the dictionary.%

The implementation of the multiset-trie is not optimized. The main reason for space-inefficiency is in implementing the links from a node to its children. A node at the $i$-th level of a tree has $n-i$ possible children where $n$ is the size of the alphabet. Our implementation uses an array data structure to link a node to its children where each element of an array includes a link to a sub-tree. A custom-implemented small and extendable hash table would significantly decrease the amount the space needed, especially since the number of children tends to decrease with the increasing levels of a tree. There are more additional optimizations possible. For example, the ...

>>>>

%The multiset-trie is an input-sensitive data structure because the size of multiset-trie $|\mathcal{M}|$ depends on the distribution of multisets in $M.$
%Our mathematical model assumes that multisets $m$ in $M$ are distributed uniformly;  however, in real-world models, such an assumption is not generally true. 
%%Specifically, the probability $P(m\in M)$ may vary dramatically and can even be equal to $0.$ For example, if words are mapped to multisets, then the sample space contains very large multisets. 
%For example, many multisets will have zero probability of appearing in $M$ because a word that would correspond to such a multiset does not exist in the dictionary.%

The implementation of the multiset-trie is not optimized. For example, the main reason for space-inefficiency is in implementing the links from a node to its children. Our implementation uses an array data structure to link a node to its children where each element of an array, indexed by the multiplicity of the element of the next level, includes a link to a sub-tree. A custom-implemented small and extendable hash table would significantly decrease the amount the space needed to represent a multiset-trie.
% There are more additional optimizations possible. For example, the ...
